Target Markdown

### 2023-11-23 _targets.Rmd
Add a method figure

>>>>

```{r plot-sim}
load(here("data","sim_for_plot"))
sim_for_plot %<>%
  select(-c(avg_cv_sp, sync)) %>%
  left_join(
    tar_read(sim_fw) %>%
      select(sim_id, ct_alive)
  )
```
```{r}
sim_for_plot %>%
  filter(env_stoch == .6, h == 2, Z == 1, S == 10, rho == 0) %>%
  arrange(desc(async))
low_z_low_rich <- sim_for_plot %>%
  filter(env_stoch == .6, Z == 1, S == 10, rho == 0) %>%
  arrange(desc(async))

tu <- timespecies_mat_to_long_tibble(low_z_low_rich$species[[1]])
plot_timeseries_lg_tbl(tu)
```

```{r}
sim_for_plot %>%
  filter(env_stoch == .6, h == 2, Z == 100, S == 10, rho == 0) %>%
  arrange(desc(async))
high_z_low_rich <- sim_for_plot %>%
  filter(env_stoch == .6, h == 2, Z == 100, S == 10, rho == 0) %>%
  arrange(desc(async))

plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(high_z_low_rich$species[[1]]))
```

```{r}
sim_for_plot %>%
  filter(env_stoch == .6, h == 2, Z == 100, S == 40, rho == 0) %>%
  arrange(desc(async))
high_z_high_rich <- sim_for_plot %>%
  filter(env_stoch == .6, h == 2, Z == 100, S == 40, rho == 0) %>%
  arrange(desc(async))
plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(high_z_high_rich))
```

```{r}
low_z_high_rich <- sim_for_plot %>%
  filter(env_stoch == .6, h == 2, Z == 1, S == 40, rho == 0) %>%
  arrange(desc(async))

low_z_high_rich_mat <- get_mat_list(low_z_high_rich)
plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(low_z_high_rich_mat[[1]]))
```

```{r}
p_low_z_low_rich <- plot_sim(x = sim_for_plot,
  id = low_z_low_rich$sim_id[[1]],
  col_palette = NULL,
  node_size_scale = .3
)
p_low_z_high_rich <- plot_sim(x = sim_for_plot,
  id = low_z_high_rich$sim_id[[2]],
  col_palette = NULL,
  node_size_scale = .5
)
p_high_z_low_rich <- plot_sim(
  x = sim_for_plot,
  id = high_z_low_rich$sim_id[[1]],
  col_palette = NULL,
  node_size_scale = .3)
p_high_z_high_rich <- plot_sim(
  x = sim_for_plot,
  id = high_z_high_rich$sim_id[[1]],
  col_palette = NULL,
  node_size_scale = .4
)

p_sim_example <- plot_grid(
  p_low_z_low_rich, p_low_z_high_rich,
  p_high_z_low_rich, p_high_z_high_rich,
  labels = c("b", "", "", ""),
  align = "hv"
)

ggsave_multiple(
  paste0("p_sim_example", c(".png", ".pdf")),
  plot = p_sim_example,
  path = here::here("report", "figures"),
  scale = 2.6,
  dpi = 400,
  width = 80,
  height = 80 * .5,
  units = "mm")
```

```{r}
sim_for_plot %>%
  filter(Z == 100, env_stoch == 0.6, rho %in% c(0, 1), S == 10, h == 2) %>%
  group_by(fw_id) %>%
  summarise(n = n()) %>%
  filter(n > 1)
sim_for_plot %>%
  filter(env_stoch == 0.6, rho %in% c(0, .75), S == 10, h == 3) %>%
  group_by(fw_id) %>%
  summarise(n = n()) %>%
  filter(n > 1)
fwid <- 549
z <- 25
sim_for_plot %>%
  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho %in% c(0, 1), S == 10, h == 2)

high_resp_div_low_rich <- sim_for_plot %>%
  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho == 0)
  #filter(env_stoch == .6, Z == 1, S == 10, rho == 0) %>%
  #arrange(desc(async))
p_high_resp_div_low_rich <- plot_sim(
  x = sim_for_plot,
  id = high_resp_div_low_rich$sim_id[[1]],
  col_palette = NULL,
  node_size_scale = .2
)

low_resp_div_low_rich <- sim_for_plot %>%
  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho == 1) %>%
  arrange(desc(async))
p_low_resp_div_low_rich <- plot_sim(
  x = sim_for_plot,
  id = low_resp_div_low_rich$sim_id[[1]],
  col_palette = NULL,
  node_size_scale = .2
)

p_sim_rho_example <- plot_grid(
  p_low_resp_div_low_rich, p_high_resp_div_low_rich,
  labels = c("a", ""),
  align = "hv"
)
ggsave_multiple(
  paste0("p_sim_rho_example", c(".png", ".pdf")),
  plot = p_sim_rho_example,
  path = here::here("report", "figures"),
  scale = 2.6,
  dpi = 400,
  width = 80,
  height = 80 * .3,
  units = "mm")
```

```{r}
p_methods <- plot_grid(p_sim_rho_example, p_sim_example, nrow = 2, rel_heights = c(1, 2))
ggsave_multiple(
  paste0("p_methods", c(".png", ".pdf")),
  plot = p_methods,
  path = here::here("report", "figures"),
  scale = 2.6,
  dpi = 400,
  width = 80,
  height = 80 * .6,
  units = "mm")
```

```{r}
tar_read(sim_fw) %>%
  filter(env_stoch == .6, S == 10, Z == 100) %>%
  ggplot(aes(y = pop_stab, x = as.factor(resp_div), color = as.factor(h))) +
  geom_boxplot()
```
